---
output: github_document
---


<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```


# The `mixr` package

<!-- badges: start -->

<!-- badges: end -->




## Overview

The `mixr` package fits linear mixed-effects
models, centered around the `nlme` package. It is centered
around fitting many models of identical form, from a list of
features as the response variable.


-----------------


## Installation


```{r install-git, eval = FALSE}
remotes::install_github("stufield/mixr")
```


-----------------


## Usage

To load `mixr` simply make a call to `library()` as usual:

```{r, eval = FALSE}
library(mixr)
```


## Help summary of the package

```{r help, eval = FALSE}
library(help = mixr)
```


## Notes about the package

* The `mixr` package is easy to use.
* There is some cool stuff we can do.


-----------------


#### LICENSE


