---
output: github_document
---


<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
ver <- desc::desc_get_version(".")
ver <- paste0("https://img.shields.io/badge/Version-", ver,
              "-success.svg?style=flat&logo=github")
```


# The `mixr` package

<!-- badges: start -->
![GitHub version](`r ver`)
[![CRAN status](http://www.r-pkg.org/badges/version/mixr)](https://cran.r-project.org/package=mixr)
[![R-CMD-check](https://github.com/stufield/mixr/workflows/R-CMD-check/badge.svg)](https://github.com/stufield/mixr/actions)
[![](https://cranlogs.r-pkg.org/badges/grand-total/mixr)](https://cran.r-project.org/package=mixr)
[![Codecov test coverage](https://codecov.io/gh/stufield/mixr/branch/main/graph/badge.svg)](https://app.codecov.io/gh/stufield/mixr?branch=main)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg)](https://choosealicense.com/licenses/mit/)
<!-- badges: end -->




## Overview

The `mixr` package fits linear mixed-effects
models, centered around the `nlme` package. It is centered
around fitting many models of identical form, from a list of
features as the response variable.


-----------------


## Installation


```{r install-git, eval = FALSE}
# current dev version
remotes::install_github("stufield/mixr")

# or a specific version
remotes::install_github("stufield/mixr@v0.0.1")
```


-----------------


## Usage

To load `mixr` simply make a call to `library()` as usual:

```{r, eval = FALSE}
library(mixr)
```


## Help summary of the package

```{r help, eval = FALSE}
library(help = mixr)
```


## Notes about the package

* The `mixr` package is easy to use.
* There is some cool stuff we can do.



